---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r, echo=TRUE}
activity<-read.csv("activity.csv")
install.packages("lubridate")
library(lubridate)
activity$date<-ymd(activity$date)
activity$interval<-as.factor(activity$interval)
```

## What is mean total number of steps taken per day?

*Histogram of the total number of steps taken each day*

```{r, echo=TRUE}
library(dplyr)
activity<-group_by(activity,date)
activity_group<-summarise(activity, sum(steps, na.rm = T))
hist(activity_group$`sum(steps, na.rm = T)`,breaks = 20)
```

*Mean and median number of steps taken each day*

```{r,echo=TRUE, results="hide"}
mean_activity<-mean(activity_group$`sum(steps)`,na.rm = TRUE )
median_activity<-median(activity_group$`sum(steps)`,na.rm = TRUE)
```

The mean was `mean_activity` and the median was `median_activity`

## What is the average daily activity pattern?

*Time series plot of the 5-minute interval and the average number of steps taken, averaged across all days*

```{r,echo=TRUE}
activity_2<-group_by(activity,interval)
activity_group_2<-summarise(activity_2, average=mean(steps, na.rm = T))
activity_group_2$interval<-as.character(activity_group_2$interval)
activity_group_2$interval<-as.numeric(activity_group_2$interval)

plot(activity_group_2$interval,activity_group_2$average, type="l")
```

*The 5-minute interval that, on average, contains the maximum number of steps*

```{r, echo=TRUE}
activity_group_2[which.max(activity_group_2$average),]
```

## Imputing missing values

*Number of missing values in the dataset*

```{r, echo=TRUE}
number_na<-is.na(activity$steps)
number_na_2<-sum(number_na)
```

The number of NA's is `number_na_2`.

*Strategy for filling in all of the missing values in the dataset*

```{r, echo=TRUE}
for (i in 1:nrow(activity)) {
        if (is.na(activity$steps[i])) {
        activity$steps[i] <- mean
        (activity$steps[activity$interval==activity$interval[i]], na.rm = TRUE)
        }
}
```

In this case, it was used the mean for each 5-minute interval.

*Histogram of the total number of steps taken each day*

```{r, echo=TRUE}
activity<-group_by(activity,date)
activity_group_3<-summarise(activity, sum(steps))
hist(activity_group_3$`sum(steps, na.rm = T)`,breaks = 20)
```

*Mean and median number of steps taken each day*

```{r, echo=TRUE}
mean_activity_2<-mean(activity_group_3$`sum(steps)`)
median_activity_2<-median(activity_group_3$`sum(steps)`)
```

The mean was `mean_activity_2` and the median was `median_activity_2`

### Do these values differ from the estimates from the first part of the assignment?





### What is the impact of imputing missing data on the estimates of the total daily number of steps?



*Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends*

```{r, echo=TRUE}
activity<-mutate(activity, weekday=weekdays(date))
weekday<-c("Monday","Tuesday","Wednesday","Thursday","Friday")
weekend<-c("Saturday","Sunday")
for (i in 1:nrow(activity)) {
        if (activity$weekday[i] %in% weekday) {
                activity$weekday[i]<-"weekday"
        } 
        if(activity$weekday[i] %in% weekend)
                {activity$weekday[i]<-"weekend"}
}
activity_4<-group_by(activity,interval,weekday)
activity_group_4<-summarise(activity_4, average=mean(steps))
activity_group_4$interval<-as.character(activity_group_4$interval)
activity_group_4$interval<-as.numeric(activity_group_4$interval)
library(ggplot2)
ggplot(activity_group_4,aes(interval,average))+geom_line()+facet_grid(.~weekday)
```

## Are there differences in activity patterns between weekdays and weekends?
